% documentclass sets the layout of this document
% article: short documents without chapters
% report: longer documents with chapters, single-sided printing
% book: longer documents with chapters, double-sided printing, with front- and back-matter (for example an index)
% letter: correspondence with no sections
% slides: for presentations (but see below)
\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{clrscode4e} % Algorithm template from Introduction to Algorithms 4th

\begin{document}
\section{Title of the first sections}

Text in the first section.

\subsection{Title of the subsection}

Text in the subsection.

\subsubsection{Title of the subsubsection}

Text in this subsubsection.

\subsubsection{Ordered list}

\begin{enumerate}
  \item 1st entry
  \item 2nd entry
  \item 3rd entry
\end{enumerate}


\subsubsection{Unordered list}

\begin{itemize}
  \item 1st entry
  \item 2nd entry
  \item 3rd entry
\end{itemize}

\subsubsection{Paragraph}

\paragraph{
  yeah sir. A quick brown fox jump over a lazy dog.
}

\subsubsection{Subparagraph}

\subparagraph{
  Oh wow. A quick brown fox jump over a lazy dog.
}

\section{Some words}

This is a lot of filler which is going to demonstrate how LaTeX hyphenates
material, and which will be able to give us at least one hyphenation point.
This is a lot of filler which is going to demonstrate how LaTeX hyphenates
material, and which will be able to give us at least one hyphenation point.

\section{Math!}

\subsection{Asymptotic Notation}

\begin{enumerate}
  \item Big O notation: $\mathcal{O}(n)$
  \item Big Theta notation: $\Theta(n)$
  \item Big Omega notation: $\Omega(n)$
\end{enumerate}

\begin{quote}
  test quote
\end{quote}

\textbf{oh wow}

\[
  \frac{n + 1}{n + 2}
\]

$\left(x + y\right)$

Using equation environment:

\begin{equation}
  \frac{n + 1}{n + 2}
\end{equation}

Test continuous mode

\subsection{Algorithms}

\begin{codebox}
\Procname{$\proc{Insertion-Sort}(A)$}
\li \For $j \gets 2$ \To $\attrib{A}{length}$
\li \Do
$\id{key} \gets A[j]$
\li \Comment Insert $A[j]$ into the sorted sequence
$A[1 \twodots j-1]$.
\li $i \gets j-1$
\li \While $i > 0$ and $A[i] > \id{key}$
\li \Do
$A[i+1] \gets A[i]$
\li $i \gets i-1$
\End
\li $A[i+1] \gets \id{key}$
\End
\end{codebox}

This is my first \LaTeX\ typesetting example.

\end{document}


